---
title: "Introduction to Data Science - HW 2"
author: "First Name Last name - `flastname@floridapoly.edu`"
output: html_notebook
---



# Problem 1 (30 points)

During class you completed an activity in which you practiced `git` commands and operations (such as forking a repository, cloning it using `git clone`, and uploading changes using `git push`).

In this exercise you are asked to modify the `flpoly_student.md` file you worked during class, and format it using the **markdown** tools discussed in class. You must **create a table** that shows the courses you are currently enrolled in, using for the headers of the table: 

| # Lean Operations Management           |
| :----:		                  |
|Kaizen               |
|Kanban               |
|Lean thinking and implementation              |
|[](https://www.investopedia.com/terms/k/kaizen.asp#:~:text=Kaizen%20is%20a%20Japanese%20term,a%20gradual%20and%20methodical%20process.) |

| # Health Services Engineering            |
| :----:		                  |
|Hurwitz Method and data analysis              |
|EOL and EOC            |
|Learning how to create pivot tables in Excel|
|[](https://www.javatpoint.com/control-system-routh-hurwitz-stability-criterion#:~:text=Routh%20Hurwitz%20criterion%20states%20that,characteristic%20equation%20in%20the%20right)| 

a. Make sure your GitHub repo (`flpoly_ds_course/`) shows the results of your updated file (remember to use the commands `git add .` , `git commit -m "YOUR MESSAGE"`, and `git push`) 

b. Include a link to your GitHub repo in this document.

c. Take a screenshot of the GitHub repo, add the screenshot file to the repo, and include it in this document (review how to insert a picture using markdown)


# Problem 2 (30 points)

For this problem, you are asked to create a list of **3 concepts** you have learned about so far this semester, for at least 2 of the courses you are currently taking. Include the name of the course as a sub-heading (that is, using `##`), and the concepts as an unordered list. Include a link to information about at least one of the concept you listed (for example a link to the Wikipedia page about that concept/topics).

_Edit this `.Rmd` file to include the solutions here._



# Problem 3 (40 points)

In this problem you will practice some basic R operations. Include solutions to each items by inserting a new R chunk of code (make sure you run the chunk so that the output is displayed)

(a) Create a variable called `my_name` that contains your preferred name.
```{r}
my_name <- "Arden Geffen"
```

(b) Create a variable called `name_length` that holds how many letters are in `my_name`.
```{r}
name_length <- nchar(my_name)
```
(c) Show which value is bigger: $e^\pi$ or $\pi^e$. 
```{r}
biggest_number <- 

```
(d) Define a function called `add_tree` that takes a single argument and returns a value 3 times larger than the input.

(e) Use the colon operator `:` to create a vector `v` of numbers from 10 to 49. Find the length of this vector using the `length()` function.

(f) Use the `seq()` function to produce a range of number from -5 to 10 in 0.5 increments.



